Make any stupid plot you want

### 2020-09-25 draft/intro.tex
clean up latex + remove tables I don't need 'cause found Stevens

Scatter Plot:
K - 0D disconnected points

A: (C1, C2, C3...)\mapsto (M....)
t \in A
-> preserve type operation and relation

@@

invariance: \mapto -> preserves operations/relations types
K might have symmetry -> move back and forth in time, preserved in K
symmatry in fibers -> scaled up/down, categorical,
preserved in the visual variables

@@

groups:
symmteries of K
symmetries of cartesian product of columns
each visual channel has symmtery group associated w/
orbit- space of possible visualiztions by changing the constants of each aesthetic (or f_{red}->f_{green})  
visual type might be orbit of that (orbit of function in space)->single function that can be transformed in that way
each visualization type is an orbit & then try to set up equivalence on these...

@@

\begin{table}
    \begin{tabular}{|r|r|}

    \end{tabular}
\caption{Symmetrys one the data preserved with each type of mark\cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\label{tab:symmetry_mark}
\end{table}

\begin{table}
\begin{tabular}{|r|r|}

\end{tabular}
\caption{Symmetries on variable columns C \caption{Symmetrys one the data preserved with each type of channel \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\label{tab:symmetry_channel}
\end{table}
Combining 
\begin{equation}
    \label{eg:renderer}
    R: M \mapsto P
\end{equation}
Where $P$ is the set of pixels rendered to screen ${p_{i,j} \in P}$

>>>>

Scatter Plot:
K - 0D disconnected points
\begin{multline}
A: (C1, C2, C3...)\mapsto (M....)\\
t \in A
\end{multline}

-> preserve type operation and relation

M is the disjoint collection of the output of all these transformers where the transformers preserve the relation and order.

@@

invariance: The symmetry group $A$ preserves invariance when the transforms $a \in A$ are symmetric such that $operation(column) = operation(channel)$ and $operation on data -> operation (mark)$

K might have symmetry -> move back and forth in time, preserved in K
symmatry in fibers -> scaled up/down, categorical,
preserved in the visual variables

@@

groups:
symmteries of K
symmetries of cartesian product of columns
each visual channel has symmtery group associated w/
orbit- space of possible visualiztions by changing the constants of each aesthetic (or $f_{red} \rightarrow f_{green}$)  
visual type might be orbit of that (orbit of function in space)->single function that can be transformed in that way
each visualization type is an orbit \& then try to set up equivalence on these...

@@

Steven's defines the group

Wiki: Symmetry group is the group of all transformations under which the object is invariant. 
The aesthetic transfroms $a \in A$ are a symmetry group that preserves transforms:

\begin{table}
    \label{tab:sym_mark}
    \begin{tabular}{|r|r|}
    \end{tabular}
\caption{Symmetrys one the data preserved with each type of mark\cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\end{table}

\begin{table}
    \label{tab:sym_mark}
    \begin{tabular}{|r|r|}
    \end{tabular}
\caption{Symmetrys one the data preserved with each type of mark\cite{bertinIIPropertiesGraphic2011,munznerMarksChannels}}
\end{table}

Scatter Plot:
K - 0D disconnected points
\begin{multline}
A: (C1, C2, C3...)\mapsto (M....)\\
 t \in A 
\end{multline}

-> preserve type operation and relation

Box chart: area + scatter

Combining 
\begin{equation}
    \label{eg:renderer}
    R: M \mapsto P
\end{equation}
Where $P$ is the set of pixels rendered to screen ${p_{i,j} \in P}$
